Placeholder

### 2021-03-16 Paper_Histograms.Rmd
Changed 'OCDRs' to 'OCRDs' on the retro mental health diagnosis by sample plot

dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("OCDRs" = n())

@@

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDRs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)

>>>>

dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("OCRDs" = n())

@@

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCRDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
